Tables

### 2024-11-02 docs/_tex/index.tex
added files

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

% ---------------------------
% END CUSTOM PREAMBLE STUFF
% ---------------------------
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

@@

\setstretch{2}
\subsection{Section}\label{section}

This is a simple placeholder for the manuscript's main document (Knuth
1984).

\section*{References}\label{bibliography}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{1}
\bibitem[\citeproctext]{ref-knuth84}
Knuth, Donald E. 1984. {``Literate Programming.''} \emph{Comput. J.}
27(2): 97--111.
doi:\href{https://doi.org/10.1093/comjnl/27.2.97}{10.1093/comjnl/27.2.97}.

\end{CSLReferences}

>>>>

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

@@

% ---------------------------
% END CUSTOM PREAMBLE STUFF
% ---------------------------
\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\usepackage{colortbl}
\usepackage{array}
\usepackage{anyfontsize}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\usepackage{bookmark}

@@

\setstretch{2}
\pagebreak

\subsection{Intro}\label{intro}

Here are intro words

\pagebreak

\section{Appendix}\label{appendix}

There should be nothing below here

\begin{table}

\caption{\label{tbl-desc-pdf}Description of Sample Demographics}

\centering{

\centering\begingroup\fontsize{8}{10}\selectfont

\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{20em}rr}
\toprule
Name & n & Pct\\
\midrule
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Qset}}\\
\cellcolor{gray!10}{\hspace{1em}A} & \cellcolor{gray!10}{644} & \cellcolor{gray!10}{50.04}\\
\hspace{1em}B & 643 & 49.96\\
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Age}}\\
\cellcolor{gray!10}{\hspace{1em}18-24} & \cellcolor{gray!10}{108} & \cellcolor{gray!10}{8.39}\\
\hspace{1em}25-34 & 242 & 18.80\\
\cellcolor{gray!10}{\hspace{1em}35-44} & \cellcolor{gray!10}{254} & \cellcolor{gray!10}{19.74}\\
\hspace{1em}45-54 & 226 & 17.56\\
\cellcolor{gray!10}{\hspace{1em}55-64} & \cellcolor{gray!10}{242} & \cellcolor{gray!10}{18.80}\\
\hspace{1em}65-74 & 148 & 11.50\\
\cellcolor{gray!10}{\hspace{1em}75-84} & \cellcolor{gray!10}{57} & \cellcolor{gray!10}{4.43}\\
\hspace{1em}85-92 & 10 & 0.78\\
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Gender}}\\
\cellcolor{gray!10}{\hspace{1em}Male} & \cellcolor{gray!10}{598} & \cellcolor{gray!10}{47.01}\\
\hspace{1em}Female & 658 & 51.73\\
\cellcolor{gray!10}{\hspace{1em}Other/Refused} & \cellcolor{gray!10}{16} & \cellcolor{gray!10}{1.26}\\
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Education}}\\
\hspace{1em}H.S. or less & 362 & 28.46\\
\cellcolor{gray!10}{\hspace{1em}Some college no degree} & \cellcolor{gray!10}{283} & \cellcolor{gray!10}{22.25}\\
\hspace{1em}Undergraduate level degree & 461 & 36.24\\
\cellcolor{gray!10}{\hspace{1em}Graduate level degree} & \cellcolor{gray!10}{166} & \cellcolor{gray!10}{13.05}\\
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Race}}\\
\hspace{1em}White or Caucasian & 975 & 76.65\\
\cellcolor{gray!10}{\hspace{1em}Black or African American} & \cellcolor{gray!10}{164} & \cellcolor{gray!10}{12.89}\\
\hspace{1em}American Indian & 22 & 1.73\\
\cellcolor{gray!10}{\hspace{1em}Asian} & \cellcolor{gray!10}{56} & \cellcolor{gray!10}{4.40}\\
\hspace{1em}Other & 55 & 4.32\\
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Party ID}}\\
\cellcolor{gray!10}{\hspace{1em}Republican} & \cellcolor{gray!10}{540} & \cellcolor{gray!10}{42.59}\\
\hspace{1em}Democrat & 566 & 44.64\\
\cellcolor{gray!10}{\hspace{1em}Independent} & \cellcolor{gray!10}{162} & \cellcolor{gray!10}{12.78}\\
\bottomrule
\end{tabular}}
\endgroup{}

}

\end{table}%

\textsubscript{Source:
\href{https://isaiahespi.github.io/rea-paper/index.qmd.html}{Article
Notebook}}

\begin{table}

\caption{\label{tbl-desc-pdf-2}}

\centering{

\centering\begingroup\fontsize{9}{11}\selectfont

\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{tabular}{lcccc}
\toprule
\textbf{Variable} & \textbf{N} & \makecell[c]{\textbf{Overall}\ \ \\N = 1,287} & \makecell[c]{\textbf{A}\ \ \\N = 644} & \makecell[c]{\textbf{B}\ \ \\N = 643}\\
\midrule
\cellcolor{gray!10}{\textbf{Age group, in years}} & \cellcolor{gray!10}{1,287} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{}\\
\hspace{1em}18-24 &  & 108 (8.4\%) & 47 (7.3\%) & 61 (9.5\%)\\
\cellcolor{gray!10}{\hspace{1em}25-34} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{242 (19\%)} & \cellcolor{gray!10}{117 (18\%)} & \cellcolor{gray!10}{125 (19\%)}\\
\hspace{1em}35-44 &  & 254 (20\%) & 127 (20\%) & 127 (20\%)\\
\cellcolor{gray!10}{\hspace{1em}45-54} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{226 (18\%)} & \cellcolor{gray!10}{109 (17\%)} & \cellcolor{gray!10}{117 (18\%)}\\
\hspace{1em}55-64 &  & 242 (19\%) & 127 (20\%) & 115 (18\%)\\
\cellcolor{gray!10}{\hspace{1em}65-74} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{148 (11\%)} & \cellcolor{gray!10}{83 (13\%)} & \cellcolor{gray!10}{65 (10\%)}\\
\hspace{1em}75-84 &  & 57 (4.4\%) & 27 (4.2\%) & 30 (4.7\%)\\
\cellcolor{gray!10}{\hspace{1em}85-92} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{10 (0.8\%)} & \cellcolor{gray!10}{7 (1.1\%)} & \cellcolor{gray!10}{3 (0.5\%)}\\
\textbf{Gender reported by respondent} & 1,272 &  &  & \\
\cellcolor{gray!10}{\hspace{1em}Male} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{598 (47\%)} & \cellcolor{gray!10}{300 (47\%)} & \cellcolor{gray!10}{298 (47\%)}\\
\hspace{1em}Female &  & 658 (52\%) & 333 (52\%) & 325 (51\%)\\
\cellcolor{gray!10}{\hspace{1em}Other/Refused} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{16 (1.3\%)} & \cellcolor{gray!10}{4 (0.6\%)} & \cellcolor{gray!10}{12 (1.9\%)}\\
\textbf{Primary race reported by respondent} & 1,272 &  &  & \\
\cellcolor{gray!10}{\hspace{1em}White or Caucasian} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{975 (77\%)} & \cellcolor{gray!10}{501 (79\%)} & \cellcolor{gray!10}{474 (75\%)}\\
\hspace{1em}Black or African American &  & 164 (13\%) & 76 (12\%) & 88 (14\%)\\
\cellcolor{gray!10}{\hspace{1em}American Indian} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{22 (1.7\%)} & \cellcolor{gray!10}{8 (1.3\%)} & \cellcolor{gray!10}{14 (2.2\%)}\\
\hspace{1em}Asian &  & 56 (4.4\%) & 24 (3.8\%) & 32 (5.0\%)\\
\cellcolor{gray!10}{\hspace{1em}Other} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{55 (4.3\%)} & \cellcolor{gray!10}{28 (4.4\%)} & \cellcolor{gray!10}{27 (4.3\%)}\\
\textbf{Highest level of education completed} & 1,272 &  &  & \\
\cellcolor{gray!10}{\hspace{1em}H.S. or less} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{362 (28\%)} & \cellcolor{gray!10}{183 (29\%)} & \cellcolor{gray!10}{179 (28\%)}\\
\hspace{1em}Some college no degree &  & 283 (22\%) & 145 (23\%) & 138 (22\%)\\
\cellcolor{gray!10}{\hspace{1em}Undergraduate level degree} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{461 (36\%)} & \cellcolor{gray!10}{229 (36\%)} & \cellcolor{gray!10}{232 (37\%)}\\
\hspace{1em}Graduate level degree &  & 166 (13\%) & 80 (13\%) & 86 (14\%)\\
\cellcolor{gray!10}{\textbf{partyid\_3cat}} & \cellcolor{gray!10}{1,268} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{}\\
\hspace{1em}Republican &  & 540 (43\%) & 278 (44\%) & 262 (41\%)\\
\cellcolor{gray!10}{\hspace{1em}Democrat} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{566 (45\%)} & \cellcolor{gray!10}{277 (44\%)} & \cellcolor{gray!10}{289 (46\%)}\\
\hspace{1em}Independent &  & 162 (13\%) & 78 (12\%) & 84 (13\%)\\
\cellcolor{gray!10}{\textbf{Political Ideology}} & \cellcolor{gray!10}{1,267} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{}\\
\hspace{1em}Extremely Liberal &  & 118 (9.3\%) & 67 (11\%) & 51 (8.0\%)\\
\cellcolor{gray!10}{\hspace{1em}Liberal} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{177 (14\%)} & \cellcolor{gray!10}{85 (13\%)} & \cellcolor{gray!10}{92 (15\%)}\\
\hspace{1em}Slightly liberal &  & 97 (7.7\%) & 48 (7.6\%) & 49 (7.7\%)\\
\cellcolor{gray!10}{\hspace{1em}Moderate: middle of the road} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{365 (29\%)} & \cellcolor{gray!10}{182 (29\%)} & \cellcolor{gray!10}{183 (29\%)}\\
\hspace{1em}Slightly conservative &  & 107 (8.4\%) & 45 (7.1\%) & 62 (9.8\%)\\
\cellcolor{gray!10}{\hspace{1em}Conservative} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{189 (15\%)} & \cellcolor{gray!10}{98 (15\%)} & \cellcolor{gray!10}{91 (14\%)}\\
\hspace{1em}Extremely conservative &  & 116 (9.2\%) & 62 (9.8\%) & 54 (8.5\%)\\
\cellcolor{gray!10}{\hspace{1em}Haven't thought much about this} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{98 (7.7\%)} & \cellcolor{gray!10}{46 (7.3\%)} & \cellcolor{gray!10}{52 (8.2\%)}\\
\textbf{Political Ideology, lean} & 98 &  &  & \\
\cellcolor{gray!10}{\hspace{1em}Liberal} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{11 (11\%)} & \cellcolor{gray!10}{6 (13\%)} & \cellcolor{gray!10}{5 (9.6\%)}\\
\hspace{1em}Conservative &  & 19 (19\%) & 8 (17\%) & 11 (21\%)\\
\cellcolor{gray!10}{\hspace{1em}None of these} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{68 (69\%)} & \cellcolor{gray!10}{32 (70\%)} & \cellcolor{gray!10}{36 (69\%)}\\
\textbf{Turnout in 2020} & 1,272 &  &  & \\
\cellcolor{gray!10}{\hspace{1em}I'm sure I didn't vote} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{185 (15\%)} & \cellcolor{gray!10}{93 (15\%)} & \cellcolor{gray!10}{92 (14\%)}\\
\hspace{1em}I don't think I voted &  & 64 (5.0\%) & 35 (5.5\%) & 29 (4.6\%)\\
\cellcolor{gray!10}{\hspace{1em}I think I voted} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{43 (3.4\%)} & \cellcolor{gray!10}{19 (3.0\%)} & \cellcolor{gray!10}{24 (3.8\%)}\\
\hspace{1em}Yes, I'm sure I voted &  & 920 (72\%) & 463 (73\%) & 457 (72\%)\\
\cellcolor{gray!10}{\hspace{1em}I was not eligible to vote} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{60 (4.7\%)} & \cellcolor{gray!10}{27 (4.2\%)} & \cellcolor{gray!10}{33 (5.2\%)}\\
\textbf{Vote Choice 2020} & 1,025 &  &  & \\
\cellcolor{gray!10}{\hspace{1em}Donald Trump} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{439 (43\%)} & \cellcolor{gray!10}{230 (45\%)} & \cellcolor{gray!10}{209 (41\%)}\\
\hspace{1em}Joe Biden &  & 527 (51\%) & 257 (50\%) & 270 (53\%)\\
\cellcolor{gray!10}{\hspace{1em}Other} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{59 (5.8\%)} & \cellcolor{gray!10}{28 (5.4\%)} & \cellcolor{gray!10}{31 (6.1\%)}\\
\textbf{Vote Intent 2024} & 1,270 &  &  & \\
\cellcolor{gray!10}{\hspace{1em}Yes} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{1,036 (82\%)} & \cellcolor{gray!10}{518 (82\%)} & \cellcolor{gray!10}{518 (82\%)}\\
\hspace{1em}No &  & 111 (8.7\%) & 49 (7.7\%) & 62 (9.8\%)\\
\cellcolor{gray!10}{\hspace{1em}Undecided} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{123 (9.7\%)} & \cellcolor{gray!10}{68 (11\%)} & \cellcolor{gray!10}{55 (8.7\%)}\\
\textbf{Prior service in the Armed Forces} & 1,272 &  &  & \\
\cellcolor{gray!10}{\hspace{1em}Yes} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{121 (9.5\%)} & \cellcolor{gray!10}{61 (9.6\%)} & \cellcolor{gray!10}{60 (9.4\%)}\\
\hspace{1em}No &  & 1,151 (90\%) & 576 (90\%) & 575 (91\%)\\
\cellcolor{gray!10}{\textbf{Currently serving in the Armed Forces}} & \cellcolor{gray!10}{121} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{}\\
\hspace{1em}Yes &  & 15 (12\%) & 5 (8.2\%) & 10 (17\%)\\
\cellcolor{gray!10}{\hspace{1em}No} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{106 (88\%)} & \cellcolor{gray!10}{56 (92\%)} & \cellcolor{gray!10}{50 (83\%)}\\
\textbf{Member of immediate family served or is currently serving} & 1,272 &  &  & \\
\cellcolor{gray!10}{\hspace{1em}Yes} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{439 (35\%)} & \cellcolor{gray!10}{212 (33\%)} & \cellcolor{gray!10}{227 (36\%)}\\
\hspace{1em}No &  & 833 (65\%) & 425 (67\%) & 408 (64\%)\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{1} n (\%)}\\
\end{tabular}}
\endgroup{}

}

\end{table}%

\textsubscript{Source:
\href{https://isaiahespi.github.io/rea-paper/index.qmd.html}{Article
Notebook}}

### 2024-11-02 index.qmd
updated src script
added files

## Section
This is a simple placeholder for the manuscript's main document [@knuth84].

>>>>

```{r}
#| label: setup
#| include: false

# load packages
library(tidyverse)

# load data
load("data/research-paper-data-20241029.Rdata")

# load data dictionary/codebook
codebook <- read.csv("data/survey_codebook.csv")
data_dict <- read.csv("data/data_dictionary.csv")

# also load the raw data dict for comparison
raw_spss_dict <- read.csv("data/raw_spss_dict.csv")

```

```{r}
#| label: fns
#| include: false

source(here::here('src', 'funs.R'))

```

\pagebreak

## Intro

Here are intro words

\pagebreak

# Appendix {.appendix}

::: {.content-visible when-format="html" unless-format="pdf"}

```{r}
#| label: tbl-desc
#| tbl-cap: "Description of Sample Demographics"
#| tbl-cap-location: top

# quick, informative, easy table of sample demographics w/ some other questions.
tbl.desc <- data |>  
  labelled::set_variable_labels(
    age_cat = "Age group, in years"
  ) |> 
  gtsummary::tbl_summary(
    by = qset,
    include = c(
    qset,
    age_cat, 
    gender_3cat, 
    race, 
    educ_4cat, 
    partyid_3cat,
    ideo,
    ideolean,
    voted2020,
    choice2020, 
    voteintent,
    milserv1,
    milserv2,
    milservfam),
    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"),
    type = list(milserv1 ~ "categorical",

                milserv2 ~ "categorical",
                milservfam ~"categorical"), 
    missing = "no") |> 
  gtsummary::add_n() |> 
  gtsummary::add_overall() |> 
  gtsummary::modify_header(label = "**Variable**") |> 
  gtsummary::bold_labels()

gtsummary::as_gt(tbl.desc) |>  
  gt::tab_footnote(
    footnote = "'true' Independents do not identify nor 'lean' toward either political party",
    placement = "left"
    ) |>  
  gt::cols_align(align = 'left', columns = everything()) |> 
  gt::tab_options(
    table.font.size = "small",
    data_row.padding = gt::px(1)
  )

```

:::

There should be nothing below here

::: {.content-hidden unless-format="pdf"}

```{r}
#| label: tbl-desc-pdf
#| tbl-cap: "Description of Sample Demographics"
#| tbl-cap-location: top

frqs <- data |> 
  select(qset, age_cat, gender_3cat, educ_4cat, race, partyid_3cat) |>
  map(count_prop)

demog_df <- purrr::reduce(frqs, dplyr::full_join)

kableExtra::kbl(demog_df,
                booktabs = T, 
                digits = 2,
                col.names = c("Name", "n", "Pct")) |> 
  kableExtra::pack_rows("Qset", 1, 2) |> 
  kableExtra::pack_rows("Age", 3, 10) |> 
  kableExtra::pack_rows("Gender", 11, 13) |> 
  kableExtra::pack_rows("Education", 14, 17) |> 
  kableExtra::pack_rows("Race", 18, 22) |> 
  kableExtra::pack_rows("Party ID", 23, 25) |> 
  kableExtra::kable_styling(
    latex_options = c("striped", "scale_down"),
    full_width = F,
    font_size = 8) |> 
  kableExtra::column_spec(1, width = "20em")

```

```{r}
#| label: tbl-desc-pdf-2

tbl.desc <- data |> 
  mutate(across(where(is.factor), ~forcats::fct_recode(., NULL = "-99"))) |> 
  labelled::set_variable_labels(
    age_cat = "Age group, in years",
    gender_3cat = "Gender",
    race = "Race",
    educ_4cat = "Highest level of education completed",
    milserv1 = "Prior service in the Armed Forces",
    milserv2 = "Currently serving in the Armed Forces",
    milservfam = "Member of immediate family served or is currently serving",
    voted2020 = "Turnout in 2020",
    choice2020 = "Vote Choice 2020",
    voteintent = "Vote Intent 2024",
    ideo = "Political Ideology",
    ideolean = "Political Ideology, lean",
    partyid_3cat = "Party ID"
  ) |>
  gtsummary::tbl_summary(
    by = qset,
    include = c(
      age_cat,
      gender_3cat,
      race,
      educ_4cat,
      partyid_3cat,
      ideo,
      ideolean,
      voted2020,
      choice2020,
      voteintent,
      milserv1,
      milserv2,
      milservfam
    ),
    statistic = list(gtsummary::all_categorical() ~ "{n} ({p}%)"),
    type = list(
      milserv1 ~ "categorical",

      milserv2 ~ "categorical",
      milservfam ~ "categorical"
    ),
    missing = "no"
  ) |>
  gtsummary::add_n() |>
  gtsummary::add_overall() |>
  gtsummary::modify_header(label = "**Variable**") |>
  gtsummary::bold_labels()

gtsummary::as_kable_extra(
  tbl.desc, 
  booktabs = T,
  digits = 2,
  addtl_fmt = T,
  linesep = ""
) |> 
  kableExtra::kable_styling(
    latex_options = c("striped", "scale_down"),
    font_size = 9)

```

:::

### 2024-11-02 notebooks/01-data-import-clean-process.qmd
added files

This document describes and executes the cleaning and processing of the survey data set downloaded from Qualtrics on 2024-09-11 at 11:39AM. Currently, this notebook is mainly to describe and explain the process undertaken in R to import, clean, wrangle, and transform the data set for later analysis. To see the process without all my explanatory text, see the relevant R script viewed [here](https://github.com/isaiahespi/cdce_vets/blob/80e843e8a9fa24d1d7524c76631b709f9f675876/scripts/01-data.R).

@@

# load raw SPSS export that includes display order vars
# downloaded 2024-09-11 at 11:38 AM
raw_spss <- haven::read_sav(file = "data-raw/vets_spss_do_2024-09-11_11.38.sav")

@@

## Create data dictionary/codebook

@@

>>>>

This document describes and executes the cleaning and processing of the survey data set downloaded from Qualtrics on 2024-10-23. Currently, this notebook is mainly to describe and explain the process undertaken in R to import, clean, wrangle, transform, and process the data set for later analysis. To see the process without all my explanatory text, see the relevant R script viewed [here](https://github.com/isaiahespi/rea-paper/blob/0bd7138259d244e9a046828fdcf09f2a33837b95/src/01-data.R).

@@

# load raw SPSS export (includes display order vars)
# downloaded on 2024-10-29 at 12:02 PM
raw_spss <- haven::read_sav("data-raw/VMF_Election_Worker_Recruitment_Survey_with_display_order_20241029_T12.02.sav")

@@

## Create data dictionary and Survey Codebook

@@

The data dictionary is the same as a codebook, but I also wanted to have a codebook that contained only the survey questions, variable labels (i.e., question text), responses (value labels), and associated values. So the saved `codebook` contains only the survey questions and the two grouping variables (`qset` and `group`).

```{r}
#| label: survey_codebook

# create and save survey codebook

# this includes only the survey questions: question number (var), the question
# text (label_var), the value labels (label_val), and the numeric codes (value)
codebook <- raw_spss |> 
  janitor::clean_names() |> 
  # get rid of superfluous Qualtrics columns
  # Keep Qualtrics `response_id`
  select(!1:8 & !10:17 & !265) |>
  # subset spss data set to omit the display order variables
  select(!contains("_do_")
         & !contains("_ado_")
         & !contains("_click")
         & !contains("_count")) |>
  select(contains("q"), group) |>
  surveytoolbox::data_dict()

# save codebook as .csv file in data/ directory
write.csv(codebook, file = "data/survey_codebook.csv")

### 2024-11-02 notebooks/02-tables.qmd
added files

---
title: Crosstabulations
author: Isaiah
format: 
  html: 
    code-fold: false
    code-tools: true
    code-overflow: wrap
    code-copy: true
    code-annotations: true
---

## Crosstables

>>>>

---
title: Tables
author: Isaiah
format: 
  html: 
    code-fold: false
    code-tools: true
    code-overflow: wrap
    code-copy: true
    code-annotations: true
---

```{r}
#| label: setup
#| include: false

# load packages
library(tidyverse)
library(datawizard)

# load data
load("data/research-paper-data-20241029.Rdata")

# load data dictionary/codebook
codebook <- read.csv("data/survey_codebook.csv")
data_dict <- read.csv("data/data_dictionary.csv")

# also load the raw data dict for comparison
raw_spss_dict <- read.csv("data/raw_spss_dict.csv")

## Descriptive table
```{r}
#| label: tbl-1
#| tbl-cap: "Description of Sample Demographics"
#| tbl-cap-location: top

# quick, informative, easy table of sample demographics w/ some other questions.
tbl1 <- data |>  
  labelled::set_variable_labels(
    age_cat = "Age group, in years"
  ) |> 
  gtsummary::tbl_summary(
    by = qset,
    include = c(
    qset,
    age_cat, 
    gender_3cat, 
    race, 
    educ_4cat, 
    partyid_3cat,
    ideo,
    ideolean,
    voted2020,
    choice2020, 
    voteintent,
    milserv1,
    milserv2,
    milservfam),
    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"),
    type = list(milserv1 ~ "categorical",

                milserv2 ~ "categorical",
                milservfam ~"categorical"), 
    missing = "no") |> 
  gtsummary::add_n() |> 
  gtsummary::add_overall() |> 
  gtsummary::modify_header(label = "**Variable**") |> 
  gtsummary::bold_labels()

gtsummary::as_gt(tbl1) |>  
  gt::tab_footnote(
    footnote = "'true' Independents do not identify nor 'lean' toward either political party",
    placement = "left"
    ) |>  
  gt::cols_align(align = 'left', columns = everything()) |> 
  gt::tab_options(
    table.font.size = "small",
    data_row.padding = gt::px(1)
  )

```{r}
#| label: tbl-1-pdf
#| tbl-cap: "Description of Sample Demographics"
#| tbl-cap-location: top

# compute counts and proportions
count_prop <- function(x, drop_na = TRUE, sort = FALSE){
  p <- data |>  
    count({{ x }})
  if (drop_na == FALSE){
    p |> 
      mutate(prop = n/sum(n))
  } else {
    p |> drop_na() |> 
      mutate(prop = n/sum(n)*100)
  }
}

frqs <- data |> 
  select(qset, age_cat, gender_3cat, educ_4cat, race, partyid_3cat) |>
  map(count_prop)

demog_df <- purrr::reduce(frqs, dplyr::full_join)

kableExtra::kbl(demog_df,
                booktabs = T, 
                digits = 2,
                col.names = c("Name", "n", "Pct")) |> 
  kableExtra::pack_rows("Qset", 1, 2) |> 
  kableExtra::pack_rows("Age", 3, 10) |> 
  kableExtra::pack_rows("Gender", 11, 13) |> 
  kableExtra::pack_rows("Education", 14, 17) |> 
  kableExtra::pack_rows("Race", 18, 22) |> 
  kableExtra::pack_rows("Party ID", 23, 25) |> 
  kableExtra::kable_styling(
    latex_options = c("striped", "scale_down"),
    full_width = F,
    font_size = 8) |> 
  kableExtra::column_spec(1, width = "20em")

```
## Crosstables
